SNEAP2021 Figures

### 2021-06-09 doc/SNEAP2021/SNEAP2021_figures.Rmd
Add summary table

```{r}
library(tidyverse)
library(here)
library(amstools)
library(HybridGIS)
library(patchwork)
library(broom)
```

@@

```{r carb-data}
carb_data <- map_dfr(list.files(here("data_analysed"), full.names = TRUE), read_csv) %>% 
  filter(!is.na(rec_num),
         Cur > 2) %>% 
  mutate(fm_diff = mean - fm_consensus,
         fm_sigma = sigma(mean, fm_consensus, merr),
         fmbc_diff = fm_lbc - fm_consensus,
         fmbc_sigma = sigma(fm_lbc, fm_consensus, merr))
```

@@

>>>>

```{r}
library(tidyverse)
library(here)
library(amstools)
library(HybridGIS)
library(patchwork)
library(broom)
library(gt)
```

@@

```{r carb-data}
carb_data <- map_dfr(list.files(here("data_analysed"), pattern = "USAMS", full.names = TRUE), read_csv) %>% 
  filter(!is.na(rec_num),
         Cur > 2) %>% 
  mutate(fm_diff = mean - fm_consensus,
         fm_sigma = sigma(mean, fm_consensus, merr),
         fmbc_diff = fm_lbc - fm_consensus,
         fmbc_sigma = sigma(fm_lbc, fm_consensus, merr))
```

@@

### Data table

```{r}
carb_data_sum <- carb_data %>% 
  select(-dil_factor, -sd, -exterr, -interr, -diff, -normFm, -sigma) %>% 
  rename(norm_ratio = mean,
         sig_norm_ratio = merr)
write_csv(carb_data_sum, here("data_analysed/carb_data_summary.csv"))
```
Carb data summary by type

```{r}
carb_data_sum %>% 
  mutate(Name = case_when(rec_num == 101730 ~ "LiveGas",
                          rec_num == 83028 ~ "C-1",
                          rec_num == 2138 ~ "TIRI-F",
                          rec_num == 17185 ~ "TIRI-I",
                          rec_num == 1082 ~ "C-2",
                          rec_num == 38809 ~ "NOSAMS2",
                          rec_num == 72446 ~ "DeadGas")) %>% 
  select(rec_num, Name, norm_ratio, fm_lbc, sig_norm_ratio) %>% 
  group_by(Name) %>% 
  summarize(across(c(norm_ratio, fm_lbc, sig_norm_ratio), c(mean = mean, sd = sd)), N = n()) %>%
  arrange(norm_ratio_mean) %>% 
  gt() %>% 
  fmt_number(columns = 2:7,
             decimals = 4)
```
